---
title: "An Introduction to the webshot Package"
author: "Winston Chang"
date: "`r Sys.Date()`"
output: html_document
vignette: >
  %\VignetteIndexEntry{An Introduction to the webshot Package}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: console
---

The [**webshot**](https://github.com/wch/webshot) package makes it easy to take screenshots of web pages from R. It requires an installation of the external program [PhantomJS](http://phantomjs.org) (you may use `webshot::install_phantomjs()` to install PhantomJS, if you do not want to download the binary and put it in `PATH` manually).

```{r setup, include=FALSE, warning=FALSE}
library(webshot)

knitr::opts_chunk$set(tidy = FALSE)

# Default image paths
fig_path <- local({
  i <- 0
  path <- knitr::opts_chunk$get('fig.path')
  function() {
    i <<- i + 1
    paste0(path, 'webshot', i, '.png')
  }
})

# A hack to automatically include the webshot output as images in R Markdown
shot <- function(..., file = fig_path(), FUN) {
  opts <- knitr::opts_current$get()
  if (is.null(opts$vwidth))
    vwidth <- 992
  else
    vwidth <- opts$fig.width * opts$dpi

  if (is.null(opts$vheight))
    vheight <- 744
  else
    vheight <- opts$fig.height * opts$dpi

  tryCatch({
    filepath <- FUN(..., file = file, vwidth = vwidth, vheight = vheight)

    # If phantomjs isn't installed, we'll end up here. We don't want the
    # vignette to error out because it could cause problems on CRAN on platforms
    # that don't have phantomjs installed.
    if (is.null(filepath)) {
      return(invisible())
    }

    knitr::include_graphics(filepath)
  },
  error = function(e) {
    invisible()
  })
}
webshot <- function(...) shot(..., FUN = webshot::webshot)
appshot <- function(...) shot(..., FUN = webshot::appshot)
```

The main function in this package is `webshot()`. Below are some examples of taking screenshots of the website http://rstudio.github.io/leaflet/:

```{r fig.width=9, fig.align='center'}
library(webshot)
URL <- "http://rstudio.github.io/leaflet/"
# Might need a longer delay for all assets to display
webshot(URL, delay = 0.5)

# Clip to the viewport
webshot(URL, cliprect = "viewport")

# Manual clipping rectangle
webshot(URL, cliprect = c(200, 5, 400, 300))

# Using CSS selectors to pick out regions
webshot(URL, selector = ".list-group")
webshot(URL, selector = c("#features", "#installation"))

# Expand selection region
webshot(URL, selector = "#installation", expand = c(10, 50, 0, 50))

# If multiple matches for a given selector, it uses the first match
webshot(URL, selector = "p")
webshot("https://github.com/rstudio/shiny/", selector = "ul.numbers-summary")
```

If you are familiar with JavaScript, you may run some JavaScript code on the page before taking the screenshot. Here is an example of logging into reddit:

```{r eval=FALSE}
# Send commands to eval
webshot("http://www.reddit.com/", "reddit-input.png",
  selector = c("#search", "#login_login-main"),
  eval = "casper.then(function() {
    // Check the remember me box
    this.click('#rem-login-main');
    // Enter username and password
    this.sendKeys('#login_login-main input[type=\"text\"]', 'my_username');
    this.sendKeys('#login_login-main input[type=\"password\"]', 'password');

    // Now click in the search box. This results in a box expanding below
    this.click('#search input[type=\"text\"]');
    // Wait 500ms
    this.wait(500);
  });"
)
```

You can also take screenshots of Shiny apps using the `appshot()` function, e.g.

```{r fig.align='center', eval=FALSE}
appdir <- system.file("examples", "01_hello", package="shiny")
appshot(appdir, delay = 3)
```

There are two functions `resize()` and `shrink()` to manipulate images, which require GraphicsMagick (or ImageMagick) and OptiPNG, respectively. A simple example:

```{r eval=FALSE}
# Result can be piped to other commands like resize() and shrink()
webshot("https://www.r-project.org/", "r-small.png") %>%
 resize("75%") %>%
 shrink()
```
